Zaca Fire Type Conversion

### 2020-09-20 Model Data Sheets and Code/Manuscript_Code.Rmd
minor change

replace: dataframe and response variable 
```{r}
set.seed(1127)

@@

# get best parameter values
tune_output$model

>>>>

options for the measure function: https://mlr.mlr-org.com/articles/tutorial/measures.html

replace: dataframe and response variable

tunRanger can also be used for ntree, but studies have shown that after a certain number of trees, usually a couple hundred, there is no benefit on accuracy/model fit of increasing ntree, so i fgiure just using a large number will get the same result as whatever number tuneRangere spits out. 
```{r}
set.seed(1127)

@@

# recommended parameter settings
# get best parameter values
tune_output$model
